An asymptotically normal out-of-sample test based on mixed estimation windows

### 2016-10-11 mixedwindow.tex
Add CHANGELOG to repository
I'm trying out the idea of including a change log for my
academic papers to make them more informative to casual
readers interested in my research. This commit adds one
to this repository and embeds it in the final pdf.

Closes #12
Add new code to stamp w/ git version and commit
This commit uses some new functionality introduced by the
latex-tools submodule (directory `texextra`) to automatically
generate and include version and commit information from the
git repository. This will make it much easier to keep track of
the different printouts as I'm editing.
[fix] Tw

\documentclass[12pt,fleqn]{article}
\input{VERSION}
\input{tex/setup}
\input{tex/mcDef}
\input{tex/ap}

@@

\end{abstract}
\newpage

\tableofcontents

\newpage

@@

\section{Theoretical results supporting the asymptotically normal \oos\ statistic}
\label{sec:1}

@@

This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test based on
mixed estimation windows'' \citep{Cal:15}. Define the following
additional terms:
\begin{equation*}
  F_t(\beta) = 2 (x_t'\beta - \yh_{t+1}) x_t',
\end{equation*}
$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.

Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.

@@

    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
    \begin{align*}
      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
    \end{align*}
    where the second inequality follows from \citepos{Mcl:75} maximal
    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
    Corollary 16.10). The summation converges to a constant as $T \to
    \infty$ and $(R'-1)^{-2\delta} \to 0$, completing the proof.

@@

\bibliography{texextra/references}
\end{document}

@@

>>>>

\documentclass[12pt,fleqn]{article}
\input{tex/setup}
\input{tex/mcDef}
\input{tex/ap}

@@

\end{abstract}
\newpage
\markboth{}{}
\tableofcontents
\newpage

@@

\section[Asymptotic normality]{Theoretical results supporting the asymptotically normal \oos\ statistic}
\label{sec:1}

@@

This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test based on
mixed estimation windows'' \citep{Cal:15}. Define the following
additional terms:
\begin{equation*}
  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
\end{equation*}
$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.

@@

    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
    \begin{align*}
      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
    \end{align*}
    where the second inequality follows from \citepos{Mcl:75} maximal
    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
    Corollary 16.10). The summation converges to a constant and
    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.

@@

\setcounter{secnumdepth}{1}
\include{CHANGELOG}

\end{document}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
